### 2016-02-17 experiments.tex
aiming to FSE

We only show results for the first 50 tests in the ranking, and computed areas under curves for the same limit, since it seems very unlikely that a user will examine many more than 50 tests, especially given the decreasing slope of the discovery curves.  In practice, after 50 tests, fixing a few faults and then re-running tests and FPF seems the most likely recourse, and we confirmed that after removing random subsets of faults, our metrics still outperform the previous best.  We applied X-means \cite{xmeans} in an attempt to use clustering, but, as with previous results \cite{PLDI13} clustering did not compare well with FPF, and the runtime was much worse than for FPF-based methods.  This tends to confirm earlier work's \cite{PLDI13} conclusion that clustering (at least based on X-means) simply does not work well in a setting with the kind of extreme disparity in instances of faults found in fuzzer taming.  A further difficulty for our setting is that X-means and most off-the-shelf clustering tools take vectors, not a distance metric.  X-means is using the raw repair data, not weighted by the fact that 0-0 agreement is much less informative than other possible matchings (recall that a Euclidean over 0-1 vectors is just the square root of Hamming distance).

@@

There were 96,828 SpiderMonkey mutants, based on 69,634 lines of code in C and header files.  Of these mutants, 12,666 were covered by some failing test case.  Of these mutants, 10,525 survived a basic set of SpiderMonkey quick tests \cite{icst2014}.  Of these mutants, 1,326 (12.6\%) repaired at least one test case.  Figure \ref{jscurves} shows the discovery curves for the mutant repair metric compared to the ideal discovery curve and the best curve from previous work using FPF, which used a normalized Levenshtein distance \cite{lev} over the failure output and test case text \cite{PLDI13}.  The APFD (Average Percent Faults Detected) values shown in the graphs are based on the measure  introduced by Rothermel et al. to evaluate test case prioritization methods \cite{APFD}.  This is a somewhat better summary of results than the raw curve areas used in previous work \cite{PLDI13}.  APFD, as the name suggests, shows the percent of all faults discovered at the ``average'' point on the curve, by comparing the curve's overall area to an ideal curve, with interpolation\footnote{The details of APFD calculation are slightly involved, and the interpolation and perfect curve are not exact fits for fuzzer taming; nonetheless the basic method summarizes curves fairly well and is standard in the testing literature for similar problems \cite{issta14}.}.

APFD results are useful summaries, but we suggest that the curve itself is also worth examining, since (1) a very good early curve is perhaps most important to developers and (2) long sequences of tests with no new faults may discourage users more than an overall less effective but steadily climbing curve with few ``plateaus'' as we call these uninformative sequences of tests.  The SpiderMonkey curve climbs very rapidly in the early portion, with perfect discovery for the first 12 faults. The largest plateau is 5 tests without a new fault, ignoring the long period after the 31st test.  In fact, a plateau at the end of the curve is not problematic.  Assuming that few users will examine more than 50 test cases without fixing some faults, the user may give up after seeing 10 or more tests without a new fault based on the mutant repair curve, and in fact lose nothing by doing so.  The PLDI 2013 curve, in contrast, has a plateau of size 17 after the 17th fault.  If we assume a user stops examining tests after a size 10 or greater plateau, the user will only see 17 faults using the PLDI 2013 metric, vs. 19 with our metric.  Dropping the stopping criteria to a plateau of size 5 produces the same results.

@@

An additional measure of effectiveness is to consider how effective a metric is in producing matched nearest neighbors.  That is, how often is the nearest neighbor of a failure (that is not due to a singleton fault --- a fault detected by only one test case) due to the same fault?  For reduced \cite{DD,PLDI13,
CReduce} test cases, we assume that for a perfect metric, the nearest neighbor should almost always share the same fault, since there is little or no extraneous semantic content to each test beyond the cause of failure.  For the SpiderMonkey failures, 96.3\% of non-singleton failures matched their nearest neighbor(s).  For mutants that repaired any failures, the mean and median number of test cases repaired were 120.6 and 4.0, respectively.  Most mutants repaired a small number of tests, but a few mutants repaired a very large number of tests.  A few mutants repaired \emph{all} SpiderMonkey faults; obviously these mutants were not actual fault fixes of any kind, but effectively disabled some mechanism {\tt jsfunfuzz} used to detect failure. The mean and median homogeneity for repairing mutants (percent of failures repaired corresponding to the most common fault repaired) were 77.96\% and 86.36\%, respectively.

@@

No method performs extremely well --- for half the faults, no methods produced what we consider a useful localization.   Compiler faults are hard to debug, and any help is useful, but it seems unlikely developers will really benefit from a localization when it does not rank at least one faulty statement in (at most) the first 20 to 30 statements.  By this measure, MUSE only provides a helpful localization once, and performs worst of the methods.  {\bf Coverage} performs very badly for three faults, and does not manage to be useful by our definition for another, but in the remaining two cases provides a good localization, in one case the best.  {\bf Repair} and MUSEUM both perform well, with {\bf Repair} slightly better.

@@

Figure \ref{fig:explain} shows part of the patch for SpiderMonkey fault 115, and the {\bf Coverage} and {\bf Repair} outputs that successfully localize the fault (the 6th coverage change output, and the 3rd mutant output), to give some idea of the information our methods present.  For {\bf Coverage}, it is surprising that the sixth highest ranked change only appeared in 5 of 148 repairs. This change ranked high out of thousands of coverage changes because it was an unusual coverage change, appearing for only 10 repairs in the entire SpiderMonkey analysis.

@@

Second, the comparison with MUSE and MUSEUM is limited.  MUSE is not really intended for multiple faults.  With our oracles, MUSE and MUSEUM may need the full results from passing tests, and some mutant we omit might be both highly ranked and a good localization.  A full comparison would include a complete analysis of passing tests also, but would likely require far more than 10x the computation time.  Finally, these experiments use Andrews' mutation operators, while MUSE/MUSEUM experiments use Proteum \cite{Proteum}, which has a much larger set of mutation operators, and their results indicate that the large set of operators is important.  However, running all Proteum GCC mutants (especially over all passing tests) would likely be very expensive.

>>>>

We only show results for the first 50 tests in the ranking, and computed areas under curves for the same limit, since it seems very unlikely that a user will examine many more than 50 tests, especially given the decreasing slope of the discovery curves.  In practice, after 50 tests, fixing a few faults and then re-running tests and FPF seems the most likely recourse, and we confirmed that after removing random subsets of faults, our metrics still outperform the previous best.  We applied X-means \cite{xmeans} in an attempt to use clustering, but, as with previous results \cite{PLDI13} clustering did not compare well with FPF, and the runtime was much worse than for FPF-based methods.  This tends to confirm earlier work's \cite{PLDI13} conclusion that clustering (at least based on X-means) simply does not work well in a setting with the kind of extreme disparity in instances of faults found in fuzzer taming.  A further difficulty for our setting is that X-means and most off-the-shelf clustering tools take vectors, not a distance metric.  X-means is using the raw repair data, not weighted by the fact that 0-0 agreement is much less informative than other possible matchings (a Euclidean over 0-1 vectors is just the square root of Hamming distance).

@@

There were 96,828 SpiderMonkey mutants, based on 69,634 lines of code in C and header files.  Of these mutants, 12,666 were covered by some failing test case.  Of these mutants, 10,525 survived a basic set of SpiderMonkey quick tests \cite{icst2014}.  Of these mutants, 1,326 (12.6\%) repaired at least one test case.  Figure \ref{jscurves} shows the discovery curves for the mutant repair metric compared to the ideal discovery curve and the best curve from previous work using FPF, which used a normalized Levenshtein distance \cite{lev} over the failure output and test case text \cite{PLDI13}.  The APFD (Average Percent Faults Detected) values shown in the graphs are based on the measure  introduced by Rothermel et al. to evaluate test case prioritization methods \cite{APFD}.  This is a somewhat better summary of results than the raw curve areas used in previous work \cite{PLDI13}.  APFD, as the name suggests, shows the percent of all faults discovered at the ``average'' point on the curve, by comparing the curve's area to an ideal curve, with interpolation\footnote{The details of APFD calculation are slightly involved, and the interpolation and perfect curve are not exact fits for fuzzer taming; nonetheless the basic method summarizes curves fairly well and is standard in the testing literature for similar problems \cite{issta14}.}.

APFD results are useful summaries, but the curve itself is also worth examining, since (1) a very good early curve is perhaps most important to developers and (2) long sequences of tests with no new faults may discourage users more than an overall less effective but steadily climbing curve with few ``plateaus'' as we call these uninformative sequences of tests.  The SpiderMonkey curve climbs very rapidly in the early portion, with perfect discovery for the first 12 faults. The largest plateau is 5 tests without a new fault, ignoring the long period after the 31st test.  In fact, a plateau at the end of the curve is not problematic.  Assuming that few users will examine more than 50 test cases without fixing some faults, the user may give up after seeing 10 or more tests without a new fault based on the mutant repair curve, and in fact lose nothing by doing so.  The PLDI 2013 curve, in contrast, has a plateau of size 17 after the 17th fault.  If we assume a user stops examining tests after a size 10 or greater plateau, the user will only see 17 faults using the PLDI 2013 metric, vs. 19 with our metric.  Stopping at a plateau of size 5 produces the same results.

@@

An additional measure of effectiveness is to consider how effective a metric is in producing matched nearest neighbors.  That is, how often is the nearest neighbor of a failure (that is not due to a singleton fault --- a fault detected by only one test case) due to the same fault?  For reduced \cite{DD,PLDI13,
CReduce} test cases, we assume that for a perfect metric, the nearest neighbor should almost always share the same fault, since there is little or no extraneous semantic content to each test beyond the cause of failure.  For the SpiderMonkey failures, 96.3\% of non-singleton failures matched their nearest neighbor(s).  For mutants that repaired any failures, the mean and median number of test cases repaired were 120.6 and 4.0, respectively.  Most mutants repaired a small number of tests, but a few mutants repaired a very large number of tests.  A few mutants repaired \emph{all} SpiderMonkey faults; obviously these mutants were not actual fault fixes, but effectively disabled some mechanism {\tt jsfunfuzz} used to detect failure. The mean and median homogeneity for repairing mutants (\% of failures repaired corresponding to the most common fault repaired) were 77.96\% and 86.36\%, respectively.

@@

No method performs extremely well --- for half the faults, no methods produced what we consider a useful localization.   Compiler faults are hard to debug, and any help is useful, but it seems unlikely developers will really benefit from a localization when it does not rank at least one faulty statement in the first 20 to 30 statements.  By this measure, MUSE only provides a helpful localization once, and performs worst of the methods.  {\bf Coverage} performs very badly for three faults, does not manage to be useful by our definition for another, and in the remaining two cases provides a good localization, in one case the best.  {\bf Repair} and MUSEUM both perform well, with {\bf Repair} slightly better.

@@

Figure \ref{fig:explain} shows part of the patch for SpiderMonkey fault 115, and the {\bf Coverage} and {\bf Repair} outputs that successfully localize the fault (the 6th coverage change output, and the 3rd mutant output), to give some idea of the information our methods present.  For {\bf Coverage}, it is surprising that the sixth highest ranked change only appeared in 5 of 148 repairs. This change ranked high out of thousands of changes because it was unusual, appearing for only 10 repairs in the entire SpiderMonkey analysis.

@@

Second, the comparison with MUSE and MUSEUM is limited.  MUSE is not really intended for multiple faults.  With our oracles, MUSE and MUSEUM may need the full results from passing tests, and some mutant we omit might be both highly ranked and a good localization.  A full comparison would include a complete analysis of passing tests also, but would likely require far more than 10x the computation time.  Finally, these experiments use Andrews' mutation operators, while MUSE/MUSEUM experiments use Proteum \cite{Proteum}, which has a much larger set of mutation operators, and their results indicate that the large set of operators is important.  However, running all Proteum GCC mutants over all passing tests would likely be prohibitively expensive.
